The Anatomy of a Temporal Summarization System

### 2015-02-28 results.tex
Latest rev ck

Table~\ref{tab:rouge} shows our results for the retrospective evaluation using ROUGE. 
AP+Salience shows improvement on ngram precision and recall over the 
baselines. This improvement is statistically significant for all ngram and longest common substring
precision, recall, and F-measure
at the $\alpha = .01$ level
using the Wilcoxon signed-rank test.

AP+Salience maintains its performance above the baselines over time as well. Figure~\ref{fig:trouge}
shows the ROUGE-1 scores over time. 
We emphasize the difference in unigram precision (bigram precision is not shown but it follows
similar curve).
Within the initial days of the event, AP+Salience is able to take the lead over the over 
systems in ngram precision. 
The AP+Salience model is better able to find salient updates
earlier on; for the disaster domain, this is an especially important quality of the model.

@@

\subsection{Expected Gain and Comprehensiveness}

@@

Table~\ref{tab:farouge} shows the results of our feature ablation
tests. Removing the language models yields a statistically 
significant drop in both ngram recall and F-measure. 
Interestingly, removing the basic features leads to an
increase in both unigram and bigram precision; in the bigram
case this is enough to cause a statistically significant increase
in F-measure over the full model. In other words, the generic features
actually lead to an inferior model when we can incorporate more appropriate
domain specific features. \ckcomment{Kathy: maybe we should mention Spark Jones here about the idea that there is no such thing as generic summarization?}

\begin{figure}
  \includegraphics[]{nuggets-metrics.eps}
\caption{Avg. Gain and Comprehensiveness performance.}
\label{fig:nperf}
\end{figure}

>>>>

Table~\ref{tab:rouge} shows our results for system output samples against the full summary of nuggets using ROUGE. 
%shows our results for the evaluation using ROUGE. 
%AP+Salience shows improvement on ngram precision and recall over the 
%baselines. 
This improvement is statistically significant for all ngram and longest common substring
precision, recall, and F-measure
at the $\alpha = .01$ level
using the Wilcoxon signed-rank test.

AP+Salience maintains its performance above the baselines over time as well. Figure~\ref{fig:trouge}
shows the ROUGE-1 scores over time. 
We show the difference in unigram precision (bigram precision is not shown but it follows
similar curve).
Within the initial days of the event, AP+Salience is able to take the lead over the over 
systems in ngram precision. 
The AP+Salience model is better able to find salient updates
earlier on; for the disaster domain, this is an especially important quality of the model.

@@

\subsection{Expected Gain and Comprehensiveness}
\begin{figure}
  \includegraphics[]{nuggets-metrics.eps}
\caption{Expected Gain and Comprehensiveness performance.}
\label{fig:nperf}
\end{figure}

@@

Table~\ref{tab:farouge} shows the results of our feature ablation
tests. Removing the language models yields a statistically 
significant drop in both ngram recall and F-measure. 
Interestingly, removing the basic features leads to an
increase in both unigram and bigram precision; in the bigram
case this is enough to cause a statistically significant increase
in F-measure over the full model. In other words, the generic features
actually lead to an inferior model when we can incorporate more appropriate
domain specific features.
This result mirrors Sparck Jones' claim that summarization should be in service of a purpose~\cite{?}.

Removing the language model and geographic relevance features leads to a
statistically significant drop in ROUGE-1 F1 scores. Unfortunately,
this is not the case for the temporal relevance features. We surmise that
these features are too strongly correlated with each other, 
i.e. the differences in TFIDF between hours are definitely not IID variables.
